The complex network of trophic interactions in a subAntarctic Marine Protected

### 2023-01-27 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Intro advance

Introduction to MPAs and MPA N-BB

Ecological importance of MPA N-BB to the region

Trophic ecology & keystone spp knowledge of B Burdwood

Why using a network approach

In the present work we present the first, detailed analysis of the food web for the MPA Namuncurá - Banco Burdwood ecosystem. For this we applied a network approach to a highly-resolved food web. The objective was twofold: characterise the food web in terms of complexity and structure, and describe the species' role in such network framework.

@@

The MPA Namuncurá - Banco Burdwood is a shallow submarine plateau called Burdwood Bank (BB) located 150 km east of Isla de los Estados and 200 km south from Malvinas/Falkland Islands (Figure 1). It comprises nearly 34.000 km^2^ circumscribed by the 200 m isobath, between 54º–55ºS and 56º–62ºW, with a slight slope extended nearly 370 km east–west. The BB is surrounded by steep flanks of more than 3000 m depth through which strong currents circulate [@Piola1989; @Reta2014; @Matano2019]. Intense upwelling and mixing occur over it, entraining deep nutrient rich waters into the photic layer [@Piola2009; @Matano2019], and resulting in a fairly homogeneous water column both spatially and temporally [@Glorioso1995; @Guerrero1999; @Matano2019]. Physical features in the MPAN-BB are fairly stable, with salinity averaging 34 all year round and temperature ranging between 4 and 8ºC overall [@Guerrero1999; @Acha2004; @Piola2009].

>>>>

* Introduction to MPAs and MPA N-BB

The evidence of benefits provided by Marine Protected Areas (MPAs) as well as the urgent need for ocean protection have driven an unprecedented increase in the number of MPAs worldwide in recent years [@Roberts2017; @Sala2018]. Globally, the total area of the world ocean designated under marine protection adds up to nearly 29,600,000 km^2^, distributed across nearly 18,444 MPAs and covering 8.16% of the ocean’s surface [@IUCN2023], and therefore approaching the 10% goal of the Convention of Biological Diversity [@CBD2004]. Despite this progress, recent reports have shown that effective protection has been overestimated because it includes areas that are not yet effectively protected (only declared) as well as areas that allow significant extractive activities [@Sala2018].

In the subAntarctic region, the level of protection is mainly associated to islands, such as South Georgia and the South Sandwich, Bouvet, Prince Edward, and Macquarie [@IUCN2023]. Interestingly, the case of the MPA Namuncurá - Banco Burdwood I (MPA N-BB), which forms the focus of this work, is unique since it is associated to a submarine plateau [@Reta2014]. Here it's noteworthy to mark that this MPA is part of a network of protected areas in the subAntarctic (i.e MPA Namuncurá - Banco Burdwood II and Yaganes), that contribute to protect and strengthen the functioning of this southern region to maintain global ocean health.

* Ecological importance of MPA N-BB to the region

Many of these MPAs centre on the presence of particularly vulnerable, keystone, or charismatic species; the presence of large numbers (or proportions) of endemic species; and the presence of high biodiversity across taxonomic levels [@Hogg2016]. Indeed, the MPA N-BB has been created because it is considered a biodiversity hotspot, mostly of its benthic community [@Schejter2016; @Falabella2017]. This community is characterized by a high biomass of vulnerable and fragile species (mainly Porifera and Cnidaria) that meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present taxa with a minimum biomass of 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResources2009]. Also, it provides habitat to several small-sized species [@Lopez-Gappa2018; @MartinSirito2019; @Schejter2019], and has an important role in the life history of fishes as a food source, refuge, or nursery area [@GarciaAlonso2018; @Delpiani2020; @Troccoli2020]. The maintenance of this singular community is related to the oceanographic processes, including the circulation of the rich Malvinas (Falkland) current in the area [@Piola1989; @Guerrero1999] and the upwelling and mixing phenomena [@Matano2019]. The input of nutrients coming from the Malvinas (Falkland) current supports the plankton community [@Guinder2020]. Overall, at the ecosystem level the MPA N-BB is ascribed as a carbon-sinker [@Bergagna2019].

* Trophic ecology & keystone spp knowledge of B Burdwood

We found that BC and BB have a more pronounced WW structure compared to CA. We identified species at mid to low trophic positions that play a key role in the trophodynamics of each marine area (e.g. Fuegian sprat Sprattus fuegensis, longtail southern cod Patagonotothen ramsayi and squat lobster Munida gregaria) and considered them as the most plausible WW species. The identification of the most influential species within food webs has become a crucial task for conservation purposes in local and regional contexts to maintain ecosystem integrity and the supply of ecosystem services for the southwestern South Atlantic Ocean. [@Riccialdelli2020]

* Why using a network approach

Anthropogenic and climate-induced impacts are known to affect individual species, but they can also change the interactions that each species has with its prey and predators (Constable et al. 2014, Lynam et al. 2017).

* Objective
In the present work we present the first, detailed analysis of the food web for the MPA N-BB ecosystem. For this we applied a network approach to a highly-resolved food web. The objective was twofold: characterise the food web in terms of complexity and structure, and describe the species' role in such network framework.

@@

The MPA Namuncurá - Banco Burdwood I is a shallow submarine plateau called Burdwood Bank (BB) located 150 km east of Isla de los Estados and 200 km south from Malvinas/Falkland Islands (Figure 1). It comprises nearly 34,000 km^2^ circumscribed by the 200 m isobath, between 54º–55ºS and 56º–62ºW, with a slight slope extended nearly 370 km east–west. The BB is surrounded by steep flanks of more than 3000 m depth through which strong currents circulate [@Piola1989; @Reta2014; @Matano2019]. Intense upwelling and mixing occur over it, entraining deep nutrient rich waters into the photic layer [@Piola2009; @Matano2019], and resulting in a fairly homogeneous water column both spatially and temporally [@Glorioso1995; @Guerrero1999; @Matano2019]. Physical features in the MPAN-BB are fairly stable, with salinity averaging 34 all year round and temperature ranging between 4 and 8ºC overall [@Guerrero1999; @Acha2004; @Piola2009].
